### 2019-01-15 thesis_report/methods.tex
Cleaned up spectrum calculation: it is near completion

		\comment{We use a short junction approximation and neglect transverse SO.}
		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}. 
		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.
		The result is specified in Eqs.~\eqref{eq:smatrix} to~\eqref{eq:momenta_short_junction}.

		In order to get the spectrum from the S-matrix [Eq.~\eqref{eq:smatrix}] we use the main result from Ref.~\cite{beenakker1991universal} and start with a determinantal equation for the bound state energies in a SNS-junction:

@@

			To solve the system analytically, we use the Short Junction limit: we set the energy to zero.
			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.\\

>>>>

		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}. 
		The short junction limit is valid for [TODO: WHEN IS THE SHORT JUNCTION LIMIT VALID]
		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.

@@

			To solve the system analytically, we use the Short Junction limit: we set the energy to zero.
			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.
			\emph{Important note: In order to use the Andreev bound state condition, the scattering matrix must be in the [TODO: NAME OF BASIS] basis. This basis transformation has already been applied in Eqs. ~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}}\\
